---
title: "Policy simulations for Melanoma for Women with 50% Stage Shift"
output:
  word_document: default
  html_document: default
---

```{r, echo=FALSE, message=FALSE}
#--------------------------------------------------------------------------------
# Run anything of substance?
#--------------------------------------------------------------------------------
# Set default to FALSE, so it doesn't stall building the package
runNow <- TRUE
# Define nsims here
nsims <- 100
#-------------------------------------------------------------------------------
# Setup 
#-------------------------------------------------------------------------------
library(reshape)
library(parallel)
library(ggplot2)
library(knitr)
library(plyr)
library(dplyr)
library(bcimodel)
data(ex1)

#--------------------------------------------------------------------------------
# Knitr
#--------------------------------------------------------------------------------
opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
#-------------------------------------------------------------------------------
# Stats will be contained in "eafr" list object
#-------------------------------------------------------------------------------
#-------------------------------------------------------------------------------
# Stats will be contained in "colomb*" list object
#-------------------------------------------------------------------------------
lungUS <- vector('list', length=length(ex1))
names(lungUS) <- names(ex1)
propERpos<-1
pop_chars <- list(male = data.frame(male = c(0), prop = c(1)))
overd1<-0
overd2<-11
ppv<-6.5
advanced1<-77.8/100
advanced2<-61.5/100
shift<-0.79
prob_early_sc<-0.03 
prob_early_ns<-0.97
prob_adv_sc<-0.147
prob_adv_ns<-0.853
surr<-5
withinstageshift<-1
withinHR1<-0.9
withinHR2<-0.9
if(surr==5){survv<-5} else if(surr==10){survv<-10}
#-------------------------------------------------------------------------------
# Statistics for Colombia 
#-------------------------------------------------------------------------------
```

```{r}
load(file = "incidence_lung.rda")
load(file = "othercausemort.rda")
```
```{r echo=FALSE}
source("compile_naturalhistmelanoma.R",local = TRUE)
source("simpolicies_melanoma.R", local = TRUE)
source("databases_melanoma.R", local = TRUE)
source("initialize_melanoma.R", local=TRUE)
source("outcomes_melanoma.R", local=TRUE)
source("cantrance_melanoma.R", local=TRUE)
source("earlydetect_melanoma.R", local = TRUE)
source("general_melanoma.R", local = TRUE)
source("initialize_melanoma.R", local = TRUE)
source("outcomes_melanoma.R", local=TRUE)
source("parallelized_melanoma.R", local=TRUE)
source("screentreatlibrary_melanoma.R", local=TRUE)
source("systime_melanoma.R", local=TRUE)
source("treatment_melanoma.R", local=TRUE)
source("compile_nathist_lung.R", local=TRUE)
othercausemort_2017<-othercausemortality
othercausemort_2017[,5]<-2.8/3.3*othercausemort_2017[,5]
incidence_lungg<-incidence_lung
incidence_lungg[,6]<-3.1/3.3*incidence_lungg[,6]
```

## Policies to investigate

```{r}
lungUS$pol  <- data.frame(num=c(1:6),
                                    id=c('nohis','nocur','noid', 'schis','sccur','scid'),
                                    name=c('M1: No Screening-Historic Treatments',
                                           'M2: No Screening-Cur Novel Treatments',
                                           'M3: No Screening-Ideal Novel Treatments',
                                           'M4: LDCT Screening-Historic Treatments',
                                           'M5: LDCT Screening-Cur Novel Treatments',
                                           'M6: LDCT Screening-Ideal Novel Treatments'),
                                           pairnum=c(NA,NA,NA, c(1, 2, 3)),
                                           earlydetHR=c(rep(1, 3), rep(0.79, 3)),
                                           stringsAsFactors=FALSE)

kable(lungUS$pol)
```

```{r, echo=FALSE}
# Early SCLC and NSCLC mortality rates
    early.sclc.mrate.co = cumsurv_to_exprate(0.357, year=survv)
    early.nsclc.mrate.co= cumsurv_to_exprate(0.685, year=survv)
```

```{r, echo=FALSE}
  # Advanced SCLC and NSCLC mortality rates
   late.sclc.mrate.co = cumsurv_to_exprate(0.069, year=survv)
   late.nsclc.mrate.co= cumsurv_to_exprate(0.159, year=survv)
```

Converting from survival to mortality rate gives us:
```{r}
lungUS$nh<-compile_naturalhist_lung(prop_adv = advanced1, mortrates=c(early.sclc.mrate.co, early.nsclc.mrate.co, late.sclc.mrate.co, late.nsclc.mrate.co),subgroup_names = c('SCLC'=0.5, 'NSCLC'=0.5), sub_probs_early = c(prob_early_sc,prob_early_ns), sub_probs_adv =c(prob_adv_sc,prob_adv_ns))
```

```{r}
#-------------------------------------------------------------------------------
# Silently define the stageshift mapping
#-------------------------------------------------------------------------------
lungUS$map <- create_stageshift_map(lungUS$nh)
```

## Treatment

```{r}
#-------------------------------------------------------------------------------
# Silently translate policies into treatment matrix: EAST AFRICA
#-------------------------------------------------------------------------------
    #Treatment
     lungUS$tx <- data.frame(expand.grid(txSSid=c("Surgery Only",
                                                    "Chemo",
                                                    "IO Monotherapy",
                                                    "IO Combination",
                                                    "EGFR Inhibitor",
                                                    "ALK inhibitor",
                                                    "Other"),
                                              SSno=1:nrow(lungUS$nh)),
                                  stringsAsFactors=FALSE)
    ntreat <- nrow(lungUS$tx)
    ntx <- length(unique(lungUS$tx$txSSid))
    # Proportions sum to 1 within stages
    lungUS$tx <- transform(lungUS$tx, 
                                 SSid=c(rep('Early.SCLC', ntx), rep('Early.NSCLC', ntx), 
                                        rep('Advanced.SCLC', ntx), rep('Advanced.NSCLC', ntx)), 
                                 txSSno=1:ntreat)
    lungUS$tx <- transform(lungUS$tx,
                                 txHR=c(1, 1, 1, 1, 1, 1, 1,
                                        1, 1, 1, 1, 1, 1, 1,
                                         1, 1, 0.7, 0.7, 1, 1, 1,
                                         1, 1, 0.66, 0.30, 0.69, 0.76, 1))
    advA <- vector('list', length=length(unique(lungUS$tx$SSid)))
    # Order of SSid: Early Advanced
    # Order of treatments: None, Interferon, Chemo, Checkpoint, Targeted
    #LDCT:
    advA[[1]] <- c(100, 0, 0, 0, 0, 0, 0)
    advA[[2]] <- c(100, 0, 0, 0, 0, 0, 0)
    advA[[3]] <- c(0,100, 0,0,0,0,0)
    advA[[4]] <- c(0,100, 0,0,0,0,0)
    # XR:
    advB<-advA
    advB[[3]] <- c(0,0,0,100,0,0,0)
    advB[[4]] <- c(0,44,22,17,14,3,0)
    advC<-advB
    advC[[3]] <- c(0,0,0,100,0,0,0)
    advC[[4]] <- c(0,0,0,76,19,5,0)
    # Put together complete vectors
    advA.v <- do.call('c', advA)
    advB.v <- do.call('c', advB)
     advC.v <- do.call('c', advC)
    props <- data.frame(advA.v,advB.v,advC.v,advA.v,advB.v,advC.v)
    
    # colSums(props)  
    colnames(props) <- lungUS$pol$id
    props2 <- props
    colnames(props2) <- lungUS$pol$name
    toprint <- data.frame(lungUS$tx, props2, stringsAsFactors=FALSE, check.names=FALSE)
    lungUS$tx <- data.frame(lungUS$tx, props, stringsAsFactors=FALSE)
    lungUS$tx <- data.frame(lungUS$tx, stringsAsFactors=FALSE)
    kable(lungUS$tx)
```

### Colombia
# Results 

## Legends and Footnotes
### Tables
Legend: Melanoma outcomes, for 100,000 men ages [insert] at the time of intervention. Results are the average across 100 simulations.
Footnote: The ARR for a given strategy is equivalent to the decrease in cumulative melanoma mortality compared to the M0 policy. Small discrepancies reflect rounding error.


```{r, message=FALSE}
#-------------------------------------------------------------------------------
# Silently run model, ages 65-80
#-------------------------------------------------------------------------------
if (runNow) {
 
    # Model
  manuscript_NLST <- simpolicies_mel(lungUS$pol, lungUS$nh, lungUS$tx,overd1,overd2,ppv,advanced1,advanced2,withinstageshift,withinHR1,withinHR2,
                                                 incsource='RISK',
                                                 mortsource='All', 
                                                 returnstats=c('mean','lower', 
                                                               'upper'), 
                                                 popsize =20000,sims=100,
                                                 futimes=c(10,25),
                                                 minage=50, maxage=80,
                                                 denom=20000)
      # Runtime
     
     # Format and save results
     detach("package:dplyr", unload = TRUE)
  
     finaltab_NLST2 <- format_bounds_list(manuscript_NLST, 
                                     paren=TRUE, includemean=TRUE, 
                                      digits=c(0,0,0,0,3,0,0,2,0,0,3),
                                     compileall=TRUE)
     write.csv(finaltab_NLST2, file=paste0('RESULTS_NLST', nsims, 'sims.csv'),
                                    row.names=FALSE)
}
```

```{r}
if (runNow) {
    kable(finaltab_NLST2)
}
```




